Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-09 paper/paper.tex
update seeds table

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,021 \\
    \smonkey\ & \cite{mozilla} & 2,116 \\
    \veight{} & \cite{v8} & 57 \\
    \midrule    
    Duktape & \cite{duktape} & 921 \\ 
    \jerry{} & \cite{jerryscript} & 1,878 \\
    JSI & \cite{jsi} & 63 \\
    Tiny-js & \cite{tinyjs} & 37 \\    
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   13 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & - & \jerry{}\\
   14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   15 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & \jerry{}\\
   16 & 8/08  & V8 & \textbf{Confirmed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccrc}
    \toprule
    Name & Source & \# JS files & \# JS files final \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 & 29,846\\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,021 \\
    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 \\
    \veight{} & \cite{v8} & 75 & 57 \\
    \midrule    
    Duktape & \cite{duktape} & 1,195 & 921\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,878\\
    JSI & \cite{jsi} & 99 & 63 \\
    Tiny-js & \cite{tinyjs} & 49 & 37 \\    
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesFilter{} \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   13 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & - & \jerry{}\\
   14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   15 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & \jerry{}\\
   16 & 8/08  & V8 & \textbf{Confirmed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   \bottomrule
  \end{tabular}
\end{table*}
